Supplementary Material to ``External Prior Guided Internal Prior Learning for Real Noisy Image Denoising"

### 2016-11-16 1047_supp.tex
a

In summary, we have the final solution of the weighted sparse coding problem (\ref{equ1}) as
\vspace{-1mm}
\begin{equation}\label{equ11}\vspace{-1mm}
\hat{\bm{\alpha}}= \text{sgn}(\mathbf{D^{T}y})\odot \text{max}(|\mathbf{D^{T}y}|-\bm{\lambda},0),
\end{equation}
where $\bm{\lambda} = \frac{1}{2}[\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\odot$ means element-wise multiplication.

>>>>

In summary, we have the final solution of the weighted sparse coding problem (\ref{equ1}) as
\vspace{-1mm}
\begin{equation}\label{equ11}\vspace{-1mm}
\hat{\bm{\alpha}}= \text{sgn}(\mathbf{D^{T}y})\odot \text{max}(|\mathbf{D^{T}y}|-\bm{\lambda},0),
\end{equation}
where $\bm{\lambda} = \frac{1}{2}[\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]^{\top}$ is the vector of regularization parameter and $\odot$ means element-wise multiplication.
